The Heavy Photon Search Test Detector

### 2013-11-11 hps-testrun-nim.tex
Johns edits to mCS section

%% main text
\section{Introduction}
\label{introduction}
One of the more striking anomalies in recent astrophysical observations is an excess of high energy electrons 
and positrons consistent with a large, unknown source of pair production~\cite{Adriani:2008zr}\cite{FermiLAT:
2011ab}. The existence of a massive, hidden sector vector boson; a ``dark photon;" that mixes kinetically with 
the Standard Model photon and mediates annihilation or decay of dark matter particles is a theoretically 
attractive explanation of this cosmic-ray excess~\cite{Holdom:1985ag}\cite{ArkaniHamed:2008qn}.
\begin{center}
{\small
\begin{figure*}[ht]
    \includegraphics[width=0.8\textwidth]{figures/hps_testrun_rendering}
\caption{Rendering of the HPS Test apparatus installed on the beam line.}
\label{fig:testrundetector}
\end{figure*}
}
\end{center}

@@

We measure the vertical angular distributions of electrons and positrons using the ECal. 
Cluster reconstruction and calibration was performed as described in Sec.~\ref{sec:ecal}. The measured 
angular distribution in the ECal for the three converter thicknesses are shown in 
Fig.~\ref{fig:ang_distr_data} (left). The data has been normalized to the integrated beam current and 
the upstream background has been subtracted. 
\begin{figure}[]
\begin{center}
{\small
%	\includegraphics[ width=7cm]{figures/rate_ecalrow_raw.png}
	\includegraphics[ width=7cm]{figures/rate_ecalrow_norm_subtr.png}
	\caption{Measured vertical angular distributions before after integrated beam current 
	normalization and upstream background subtraction.}
	\label{fig:ang_distr_data}
}
\end{center}
\end{figure}
The background fraction for the three converter thicknesses was 16\%, 52\% and 71\% 
for converter thicknesses of 1.6\%, 0.45\% and 0.18\%, respectively. The background fraction was also 
cross-checked by pointing back tracks reconstructed in the SVT to identify the fraction of tracks not originating 
from the converter. We also checked that the contribution from photons to our triggered 
sample was much less than 2\%. These measured angular distributions are compared to simulation to validate 
the modeling of the MCS. \egs{}~\cite{egs5} is used to generate 
the electromagnetic interactions in the converter while \geant{} is used to simulate the particles after the 
converter.  Figure~\ref{fig:ang_distr_dataMC} shows the angular distribution comparing data and 
\egs{} normalized to 1~s of beam at 90~nA beam current with a converter thickness of 1.6\%. 
\begin{center}
{\small
	\begin{figure}[]
%	\begin{figure*}[t]
	\includegraphics[ scale=0.25]{figures/dataMC_1351_Hit_Y_top_norm_bkgsub.png}
%	\includegraphics[ scale=0.25]{figures/dataMC_1354_Hit_Y_top_norm_bkgsub.png}
%	\includegraphics[ scale=0.25]{figures/dataMC_1353_Hit_Y_top_norm_bkgsub.png}
	\caption{Comparison between the observed and predicted angular distribution using \egs{} for a 
	converter thickness of 1.6\%. Similar agreement is found for 0.45\% and 0.18\% converter thicknesses. 
	Only statistical uncertainties are shown. }
	\label{fig:ang_distr_dataMC}
%	\end{figure*}
	\end{figure}
}
\end{center}
Reasonable agreement is obtained in the most important region close to the beam. There is a hint of a 
slightly different slope of the data at larger angles; this difference is covered by systematic uncertainties.  The 
total rates for each converter thickness is shown in Fig.~\ref{fig:rate_vs_thickness} and summarized in 
Tab.~\ref{tab:ang_distr_dataMC}.
\begin{center}
{\small
	\begin{figure}[]
%	\begin{figure*}[]
	%\includegraphics[ scale=0.3]{figures/dataMC_geant4.png}
	\includegraphics[ scale=0.3]{figures/dataMC_egs.png}
	\caption{The measured rate as a function of converter thickness for data and \egs{} simulation of MCS in 	the converter.} 
	\label{fig:rate_vs_thickness}
%	\end{figure*}
	\end{figure}
}
\end{center}
The total systematic uncertainty was estimated to be between 10-18\% depending on the run, they include:  
uncertainty on the integrated current normalization (5\%), alignment of the ECal, uncertainty from the 
background normalization and limited Monte Carlo statistics.  
\begin{table}
\begin{center}
{\small
\begin{tabular}{|l|c|c|c|}
\hline
Converter (\% $X_0$) & 1.60 & 0.45 &	0.18 \\
\hline
\egs{} &	1162 $\pm$ 112 &	255 $\pm$ 28 &	94 $\pm$ 17	\\
\hline
\geant{} & 2633 $\pm$ 250 & 	371 $\pm$ 38 &	114 $\pm$ 18 \\
\hline
Observed 	& 1064 $\pm$ 2 & 196 $\pm$ 1 &	92 $\pm$ 1 \\						
\hline
\end{tabular}
\caption{ Observed and predicted number of events for 1~s of beam at 90~nA for three different converter 
thicknesses. The uncertainty on the prediction includes systematic uncertainties. }
\label{tab:ang_distr_dataMC}
}
\end{center}
\end{table}
As expected \egs{} show good agreement with our data while \geant{} using the default physics list 
overestimates the MCS at these large angles.

>>>>

%% main text
\section{Introduction}
\label{introduction}
One of the more striking anomalies in recent astrophysical observations is an excess of high energy electrons 
and positrons consistent with a large, unknown source of pair 
production~\cite{Adriani:2008zr,FermiLAT:2011ab}. 
The existence of a massive, hidden sector vector boson; a ``dark photon;" that mixes kinetically with 
the Standard Model photon and mediates annihilation or decay of dark matter particles is a theoretically 
attractive explanation of this cosmic-ray excess~\cite{Holdom:1985ag}\cite{ArkaniHamed:2008qn}.
\begin{center}
{\small
\begin{figure*}[ht]
    \includegraphics[width=0.8\textwidth]{figures/hps_testrun_rendering}
\caption{Rendering of the HPS Test apparatus installed on the beam line.}
\label{fig:testrundetector}
\end{figure*}
}
\end{center}

@@

For this analysis, we measure angular distribution of electrons and positrons using the ECal.
Cluster reconstruction was done using the algorithm described in Sec.~\ref{sec:trigger} build 
clusters around seed hits (hits above a ``seed'' energy threshold and with greater energy than any 
neighboring hits), and add all neighboring hits above an ``add'' energy threshold.
Hit energy is calibrated by matching track momentum to cluster energy, as described in Sec.~\ref{sec:ecal_calibration}.

The measured 
angular distribution in the ECal for the three converter thicknesses are shown in 
Fig.~\ref{fig:ang_distr_data} (left). 
\begin{figure}[]
\begin{center}
{\small
%	\includegraphics[ width=7cm]{figures/rate_ecalrow_raw.png}
	\includegraphics[ width=7cm]{figures/rate_ecalrow_norm_subtr.png}
	\caption{Measured vertical angular distributions after integrated beam current 
	normalization and background subtraction.}
	\label{fig:ang_distr_data}
}
\end{center}
\end{figure}
The data has been normalized to the integrated beam current and the background has been 
subtracted. 
The background fraction for the there converter thicknesses was 16\%, 52\% and 71\% 
for converter thicknesses of 1.6\%, 0.45\% and 0.18\%, respectively. The background fraction was also 
cross-checked by pointing back tracks reconstructed in the SVT to identify the fraction of tracks not emanating from the converter. 
%This can be seen in Fig.~\ref{fig:extrapol_converter} (bottom) where small 
%satellite peaks at $\pm 10$~mm can be identified as tracks from the upstream background. The angular distribution, after normalization and subtracting the upstream background, are shown in 
%Fig.~\ref{fig:ang_distr_data} (right).  
We also checked that the contribution from photons to our triggered 
sample was less than 2\% (without angular selections which would further reduce the contribution).

These measured angular distributions are compared to simulation to validate 
the modeling of the MCS. \egs{}~\cite{egs5} is used to generate 
the electromagnetic interactions in the converter while \geant{} is used to simulate the particles after the 
converter.  Figure~\ref{fig:ang_distr_dataMC} shows the angular distribution comparing data and 
\egs{} normalized to 1~s of beam at 90~nA beam current with a converter thickness of 1.6\%. 
\begin{center}
{\small
	\begin{figure}[]
%	\begin{figure*}[t]
	\includegraphics[ scale=0.25]{figures/dataMC_1351_Hit_Y_top_norm_bkgsub.png}
%	\includegraphics[ scale=0.25]{figures/dataMC_1354_Hit_Y_top_norm_bkgsub.png}
%	\includegraphics[ scale=0.25]{figures/dataMC_1353_Hit_Y_top_norm_bkgsub.png}
	\caption{Comparison between the observed and predicted angular distribution using \egs{} for a 
	converter thickness of 1.6\%. Similar agreement is found for 0.45\% and 0.18\% converter thicknesses. 
	Only statistical uncertainties are shown. }
	\label{fig:ang_distr_dataMC}
%	\end{figure*}
	\end{figure}
}
\end{center}
Reasonable agreement is obtained in the most important region close to the beam. There is a hint of a 
slightly different slope of the data at larger angles; this difference is covered by systematic uncertainties.  The 
total rates for each converter thickness is shown in Fig.~\ref{fig:rate_vs_thickness} and summarized in 
Tab.~\ref{tab:ang_distr_dataMC}.
\begin{center}
{\small
	\begin{figure}[]
%	\begin{figure*}[]
	%\includegraphics[ scale=0.3]{figures/dataMC_geant4.png}
	\includegraphics[ scale=0.3]{figures/dataMC_egs.png}
	\caption{The measured rate as a function of converter thickness for data and \egs{} simulation of MCS in 	the converter.} 
	\label{fig:rate_vs_thickness}
%	\end{figure*}
	\end{figure}
}
\end{center}
The total systematic uncertainty was estimated to be between 10-18\% depending on the run including:  
a 5\% uncertainty on the integrated current normalization, alignment of the ECal, uncertainty from the 
background normalization, and limited Monte Carlo statistics.  
\begin{center}
{\small
\begin{table}
\begin{tabular}{|l|c|c|c|}
\hline
Converter (\% r.l.) & 1.60 & 0.45 &	0.18 \\
\hline
EGS5 &	1162 $\pm$ 112 &	255 $\pm$ 28 &	94 $\pm$ 17	\\
\hline
GEANT4 & 2633 $\pm$ 250 & 	371 $\pm$ 38 &	114 $\pm$ 18 \\
\hline
Observed 	& 1064 $\pm$ 2 & 196 $\pm$ 1 &	92 $\pm$ 1 \\						
\hline
\end{tabular}
\caption{ Observed and predicted number of events for 1~s of beam at 90~nA for three different converter 
thicknesses. The uncertainty on the prediction includes systematic uncertainties. }
\label{tab:ang_distr_dataMC}
\end{table}
}
\end{center}
